\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[top=0.75in, left=0.75in, right=0.75in, bottom=0.75in]{geometry}
\author{John Muschelli}

\begin{document}
\thispagestyle{empty}

\begin{center}
{\bf
{\large Statement of Contributions to Diversity }\\
John Muschelli
}
\end{center}

For the past 5 years, I have volunteered with the organization Thread (formerly the Incentive Mentoring Program).  Thread started out as a single Johns Hopkins graduate student mentoring 5 students at a nearby high school and now has over 500 volunteer members, over 15 staff, and is a full non-profit organization.  A goal of Thread is to help students in Baltimore City succeed by reducing psychological, social, and practical challenges.  As volunteers, we help students with coursework, any life struggles, drive students to school, and provide a support system that is lacking for many.  

Personally, I have been a volunteer/mentor, a head of family which is a manager, and a grandparent which is a middle manager between heads of families and the site director.  As a grandparent, I oversee 7 families, which serve 7 high school and post-high-school students.  Specifically, I have been involved with one student for the last 5 years.  I have been involved with all aspects of this student: mentoring him personally during high school, helping him graduate his senior year, and helping him obtain a job after high school.  

Overall, I would like to continue to serve the community in a similar aspect.  I have found this volunteer work to be some of the most rewarding aspects of my graduate career and would employ students to participate in similar programs.  

\end{document}

